Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-06-07 docs/paper/paper.Rmd
update forecasts + truth

- Forecast performance overview for the ensemble and surrogate.
- Forecast performance overview by forecast horizon. Highlight degrading performance with this impacting the surrogate model to a greater degree. 
- Discussion country level differences in perforamance and link to potential growth rate trends.

@@

- Figure 2:
  Sub-figure 1:
    - Density/histogram of overall relative scores + mean line
  Sub-figure 2:
    - Density/histogram of relative scores + mean line by horizon
  Sub-figure 3:
     - Density/histogram of relative scores + mean line by location

>>>>

- Forecast performance overview for the ensemble and surrogate.
- Forecast performance overview by forecast horizon. Highlight degrading performance with this impacting the surrogate model to a greater degree. 
- Discussion country level differences in performance and link to potential growth rate trends.

@@

## Relative forecast evaluation {-}

- Relative performance of surrogate model by forecast horizon.
   - Give mean relative performance difference by horizon
   - Discuss distribution.
- Relative performance of surrogate model by month stratified by forecast horizon.
  - Give mean relative performance by month for each horizon
  - Discuss distribution
- Relative performance of surrogate model by location sratified by forecast horizon.
  - Discuss qualatative differences between locations
